---
title: "test"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## First part
Q1.1) Does schizophrenia involve altercentric intrusion? *We're interested in seeing how the two diagnostic groups differ in altercentric intrusion* 
Define model and priors. 
Test the implications of your priors (prior predictive checks) and if needed adjust them. 
Run the model. 
Test the quality of the fitted model (posterior predictive checks, prior-posterior updates). 
Assess the evidence in favor of an increased altercentric intrusion in schizophrenia. Report the model and the results, including plots.

```{r}
# setup
pacman::p_load(ggplot2, 
               tidyverse, 
               rethinking, 
               brms)
# read in data
d <- read.csv("Ass2.csv")
d <- d %>% na.omit()
# making Diagnosis an index variable
d$Diagnosis <- ifelse(d$Diagnosis == 0, 1, 2)
# first look
head(d)
# scale
d$s_AltercentricIntrusion <- scale(d$AltercentricIntrusion)
# plot to see the distribution overall
d %>% ggplot(aes(s_AltercentricIntrusion))+
  theme_minimal()+
  geom_density()+
  ggtitle("Density of Altercentric intrusion scores (scaled)")
# plot to see for the two distributions og Control and Schizophrenic
d$Diagnosis_name <- ifelse(d$Diagnosis == 1, "Control", "Schizophrenic")
# get means
d %>% group_by(Diagnosis_name) %>% summarise(mean(s_AltercentricIntrusion))
d %>% group_by(Diagnosis_name) %>% 
  ggplot(aes(s_AltercentricIntrusion, fill = Diagnosis_name, color = Diagnosis_name))+
  geom_density(alpha = 0.3)+
  geom_vline(xintercept = -0.09912351	, size = 0.5, color = "red") + #control mean
  geom_vline(xintercept = 0.29737054	, size = 0.5, color = "blue") + #schizo mean
  ggtitle("Density of Altercentric intrusion scores per Diagnosis (std) w. color-coded
  mean lines")+
  theme_minimal() +
  xlab("Altercentric Intrusion severity score (std)")+
  ylab("Density")
```
From the plot we can tell that the mean for Altercentric Intrustion severity is higher for Schizophrenics (blue distribution and blue mean line) than for Controls (red distribution and red mean line). Higher peak also for the blue distribution - calculate area under curve? 

# Let's model some shit
So we want to see whether altercentric intrusion and schizophrenia hangs out together in symptom kingdom.

To do that, let's try to model Altercentric Intrusion as a gaussian distribution. We will try to predict Altercentric Intrusion amount from Diagnosis. Hypothesis is that diagnosis determines Altercentric Intrusion. 
*QUESTION: SHOULD WE TRY TO PREDICT DIAGNOSIS FROM ALTERCENTRIC INTRUSION TOO?*

```{r}
# 1. Define model
####### Gonna do it with quap first, because they do it in the book and I want to see: 
m0.quap <- quap(alist(s_AltercentricIntrusion ~ dnorm(mu, sigma),
                      mu <- a[Diagnosis],
                      a[Diagnosis] ~ dnorm(0, 5),
                      sigma ~ dexp(1)), data = d)
precis(m0.quap, depth = 2)
```

### MODEL m0
```{r}
####### Gonna do it with brms now
## define formula
AS_f0 <- bf(s_AltercentricIntrusion ~ 1 + Diagnosis)
# specify and visualize priors - what priors do we want? 
get_prior(
  AS_f0,
  d,
  family = gaussian
)
# defining priors: 
AS_p0 <- c(
  prior(normal(0,0.5), class = Intercept), 
 prior(exponential(1), class = sigma), 
 prior(normal(0,1), class = b, coef = Diagnosis) #ask about this
)
# 2. Visualize joint expectations of the model (prior + likelihood function)
## Predictive priors (ppcheck, but also conditional effects)
# model 
model_prior <- brm(
  formula = AS_f0,
  data = d,
  family = gaussian,
  prior = AS_p0,
  sample_prior = "only",
  backend = "cmdstanr",
  threads = threading(2)
)
# prior predictive check
(p0 <- pp_check(model_prior, nsamples=100)+xlab("Altercentric Intrusion (std)")+ylab("Density")+ggtitle("Prior predictive check for model m0"))
# 3. Fit the model
model <- brm(
  formula = AS_f0,
  data = d,
  family = gaussian,
  prior = AS_p0,
  sample_prior = T,
  backend = "cmdstanr",
  threads = threading(2)
)
# posterior predictive check
(p1 <- pp_check(model, nsamples=100)+xlab("Altercentric Intrusion (std)")+ylab("Density")+ggtitle("Posterior predictive check for model m0"))
# 4. Assess model quality
library(patchwork)
# prior pred. and posterior pred. 
p0 + p1
# posterior learning (update) plots
posterior <- posterior_samples(model)
ggplot(posterior) +
  theme_classic() +
  geom_density(aes(prior_Intercept), fill="red", alpha=0.3) +
  geom_density(aes(b_Intercept), fill="blue", alpha=0.5)+
  ggtitle("Posterior learning against prior (Intercept)")
ggplot(posterior) +
  theme_classic() +
  geom_density(aes(prior_sigma), fill="red", alpha=0.3) +
  geom_density(aes(sigma), fill="blue", alpha=0.5) +
  ggtitle("Posterior learning against prior (Sigma)")
ggplot(posterior) +
  theme_classic() +
  geom_density(aes(prior_b_Diagnosis), fill="red", alpha=0.3) +
  geom_density(aes(b_Diagnosis), fill="blue", alpha=0.5)+
  ggtitle("Posterior learning against prior (Beta for Diagnosis, 
  so the expected difference between populations in Altercentric Intrusion-score)")+
  geom_vline(xintercept = mean(posterior$b_Diagnosis)	, lty = 2, alpha = .7, color = "darkblue")
# conditional effects - plotting model
conditional_effects(model)
plot(conditional_effects(model), points=T)
plot(conditional_effects(model, spaghetti=T, nsamples=100, method = "fitted"), points=T)
plot(conditional_effects(model, spaghetti=T, nsamples=100, method = "predict"), points=T)
```
## wat
```{r}
hypothesis(model, "Diagnosis > 0")
hypothesis(model, "Intercept < 0")
?hypothesis
```


### MODEL m1
```{r}
####### Gonna do it with brms now - with the other model 
## define formula
AS_f1 <- bf(s_AltercentricIntrusion ~ 1 + Diagnosis)
# specify and visualize priors - what priors do we want? 
get_prior(
  AS_f1,
  d,
  family = gaussian
)
# defining priors: 
AS_p1 <- c(
  prior(normal(0,0.5), class = Intercept), 
 prior(exponential(1), class = sigma), 
 prior(normal(0,0.5), class = b, coef = Diagnosis) #ask about this
)
# 2. Visualize joint expectations of the model (prior + likelihood function)
## Predictive priors (ppcheck, but also conditional effects)
# model 
model1_prior <- brm(
  formula = AS_f1,
  data = d,
  family = gaussian,
  prior = AS_p1,
  sample_prior = "only",
  backend = "cmdstanr",
  threads = threading(2)
)
# prior predictive check
(p00 <- pp_check(model1_prior, nsamples=100)+xlab("Altercentric Intrusion (std)")+ylab("Density")+ggtitle("Prior predictive check for model m1"))
# 3. Fit the model
model1 <- brm(
  formula = AS_f1,
  data = d,
  family = gaussian,
  prior = AS_p1,
  sample_prior = T,
  backend = "cmdstanr",
  threads = threading(2)
)
# posterior predictive check
(p11 <- pp_check(model1, nsamples=100)+xlab("Altercentric Intrusion (std)")+ylab("Density")+ggtitle("Posterior predictive check for model m1"))
# 4. Assess model quality
library(patchwork)
# prior pred. and posterior pred. 
p00 + p11
# posterior learning (update) plots
posterior1 <- posterior_samples(model1)
ggplot(posterior1) +
  theme_classic() +
  geom_density(aes(prior_Intercept), fill="red", alpha=0.3) +
  geom_density(aes(b_Intercept), fill="blue", alpha=0.5)+
  ggtitle("Posterior learning against prior (Intercept)")
ggplot(posterior1) +
  theme_classic() +
  geom_density(aes(prior_sigma), fill="red", alpha=0.3) +
  geom_density(aes(sigma), fill="blue", alpha=0.5) +
  ggtitle("Posterior learning against prior (Sigma)")
ggplot(posterior1) +
  theme_classic() +
  geom_density(aes(prior_b_Diagnosis), fill="red", alpha=0.3) +
  geom_density(aes(b_Diagnosis), fill="blue", alpha=0.5)+
  ggtitle("Posterior learning against prior (Beta for Diagnosis, 
  so the expected difference between populations in Altercentric Intrusion-score)")+
  geom_vline(xintercept = mean(posterior1$b_Diagnosis)	, lty = 2, alpha = .7, color = "darkblue")
model
# conditional effects - plotting model
# conditional_effects(model)
# 
# plot(conditional_effects(model), points=T)
# 
# plot(conditional_effects(model, spaghetti=T, nsamples=100, method = "fitted"), points=T)
# 
# plot(conditional_effects(model, spaghetti=T, nsamples=100, method = "predict"), points=T)
```
## wat
```{r}
hypothesis(model, "Diagnosis > 0")
hypothesis(model, "Intercept < 0")
?hypothesis
```

*Question: When we run get_prior(AS_f0,d,family = gaussian) and the output shows b, b Diagnosis, Intercept and Sigma, do we just use get_prior to see how many prior-parameters we need? *









































```{r}
#uhmm why do the means on the plots look opposite? 
# # Checking control
# d_sub <- filter(d,d$Diagnosis==0)
# 
# d_sub %>% summarise(mean(s_AltercentricIntrusion))
# 
# d_sub %>% 
#   ggplot(aes(s_AltercentricIntrusion, fill = Diagnosis_name, color = Diagnosis_name))+
#   geom_density(alpha = 0.3)+
#   geom_vline(xintercept = -0.09912351	, size = 0.5, color = "red") + #control mean
#   #geom_vline(xintercept = 0.29737054	, size = 0.5, color = "blue") + #schizo mean
#   ggtitle("Density of Altercentric intrusion scores per Diagnosis (scaled) w. mean lines")+
#   theme_minimal()
# 
# 
# # Checking schizo
# d_sub <- filter(d,d$Diagnosis==1)
# 
# d_sub %>% summarise(mean(s_AltercentricIntrusion))
# 
# d_sub %>% 
#   ggplot(aes(s_AltercentricIntrusion, fill = Diagnosis_name, color = Diagnosis_name))+
#   geom_density(alpha = 0.3)+
#   #geom_vline(xintercept = -0.09912351	, size = 0.5, color = "red") + #control mean
#   geom_vline(xintercept = 0.29737054	, size = 0.5, color = "blue") + #schizo mean
#   ggtitle("Density of Altercentric intrusion scores per Diagnosis (scaled) w. mean lines")+
#   theme_minimal()
```