---
title: "Final"
author: "Study group 4evar"
date: "3/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Assignment 2 - Exploring causal inference issues

In this assignment we explore some issues related to multiple regressions (regressions with more than one predictor), and inferred (causal) relations between variables. N.B. the data is simulated (to make sure I know the actual mechanism generating it), but it's based on a real study. So bear with a longish introduction to get into the details of what we are doing and why it is important.

### Altercentric intrusion in schizophrenia

People with schizophrenia often report altered control and distinction of self-other representations: intrusive thoughts, hearing of voices, delusions of mind reading, paranoia, etc (a substantial portion of the psychotic symptoms experienced in schizophrenia). These have been variously attributed to hypermentalizing (over attribution of mental states to others), social impairment (over preoccupation with own thought processes), hyper socialization (inability to inhibit information from others), etc.

The current study investigates 1) whether schizophrenia is indeed related to altered control and distinction of self-other representations, in particular altercentric intrusions (inability to inhibit social information), and 2) whether these are related to the relevant psychotic symptoms. N.B. the actual study also investigates egocentric intrusion, do check the papers below if interested.

The task is a slightly modified version of this: https://www.ncbi.nlm.nih.gov/pubmed/20731512 (also what Nicole and Louise described in their guest talk) You look at a picture with some dots visible to you, as well as with a different person with a different set of dots visible to them. The number of dots you see and that the other sees can be the same (congruent condition) or not (incongruent condition). You are tasked to indicate whether a given number (e.g. 3) matches the number of dots you see (and the dots visible to the other person are irrelevant to the task).


The tasks investigates altercentric intrusion: will your reaction time change according to whether the other person is seeing the same amount of dots as you, or not? The idea is that if you correctly inhibit social information, your reaction time should not change, as the information about the other person is not relevant. On the contrary, if you nevertheless use task irrelevant social information, you'll be slower at indicating whether 3 is the right number of dots when the other person sees a different amount of dots than you (conflicting information).
The bigger the difference between RTs in the congruent and incongruent condition the bigger the altercentric intrusion effect.

For each participant you have 6 variables: 1) ID, 2) AltercentricIntrusion (continuous score), 3) Diagnosis (schizophrenia vs. control), 4) VoiceHearing (severity of voice hearing symptoms, continuous score of the severity of the symptom as measured by a clinician), 5) MindReading (severity of delusions of mind reading, continuous score of the severity of the symptom as measured by a clinician); 6) Apathy (severity of lack of motivation in taking care of oneself, from washing to showing up at work, continuous score of the severity of the symptom as measured by a clinician). 
N.B. Real clinical scores of symptoms would be on a likert scale, and altercentric intrusions would be on a slightly complex continuous scale. But life is too short for that shit, and we want to focus on multivariate models and causal inference, so all those variables in the assignment (but ID and Diagnosis) have been simulated as Gaussian distributions.

The research questions you have to answer are the following:

## First part

Q1.1) Does schizophrenia involve altercentric intrusion? 

a) Define model and priors. 
b) Test the implications of your priors (prior predictive checks) and if needed adjust them. 
c) Run the model. 
d) Test the quality of the fitted model (posterior predictive checks, prior-posterior updates). 
e) Assess the evidence in favor of an increased altercentric intrusion in schizophrenia. 
f) Report the model and the results, including plots.

```{r}
library(pacman)

p_load(dagitty, 
       tidyverse, 
       rethinking, 
       brms, 
       patchwork, 
       tidybayes)

```


```{r}
# Scaling and scaling
d <- read_csv("Ass2.csv") %>% mutate(
  ACI = scale(AltercentricIntrusion),
  MR = scale(MindReading),
  APA = scale(Apathy),
  VH = scale(VoiceHearing),
  Diagnosis = as.factor(Diagnosis + 1),
  Diagnosis_name = ifelse(d$Diagnosis == 1, "Control", "Schizophrenic"))
```

```{r}
# Density plot
dens(d$ACI) 

# Boxplot
ggplot(d, aes(x = Diagnosis, y = ACI))+
  geom_boxplot(aes(group = Diagnosis, fill = Diagnosis), alpha = .5)+
  theme_minimal()

d %>% group_by(Diagnosis_name) %>% 
  ggplot(aes(ACI, fill = Diagnosis_name, color = Diagnosis_name)) +
  geom_density(alpha = 0.3) +
  geom_vline(xintercept = -0.09912351	, size = 0.5, color = "red") + #control mean
  geom_vline(xintercept = 0.29737054	, size = 0.5, color = '#00BFC4') + #schizo mean
  ggtitle("Density of Altercentric intrusion scores per Diagnosis (std) w. color-coded
  mean lines") +
  theme_minimal() +
  xlab("Altercentric Intrusion (std)") +
  ylab("Density") + expand_limits(x = c(-3.5, 3.5)) + 
  labs(fill = "Diagnosis", colour = "Diagnosis")

```

```{r}
# brms model with index variable

# Building models
ACI_f0 <- bf(ACI ~ 0 + Diagnosis) # Is this how you would use index variables in brm? How do you interprete the outcome?

# Help getting priors
get_prior(ACI_f0,
          d,
          family = gaussian)

# Defining the priors
ACI_p0 <- c(
  prior(normal(0, 1), class = b, coef = Diagnosis1),
  prior(normal(0, 1), class = b, coef = Diagnosis2),
  prior(normal(1, 0.5), class = sigma)
)

# Building prior model
ACI_m0_prior <- brm(
  formula = ACI_f0,
  data = d,
  family = gaussian,
  prior = ACI_p0,
  #file = "ACI_m0_prior",
  sample_prior = "only",
  backend = "cmdstanr"
  #threads = threading(2)
)

# PP Check
(
  p1_m0 <- pp_check(ACI_m0_prior, nsamples = 100) +
    xlab("Altercentric Intrusion (std)") +
    ylab("Density") +
    ggtitle("Prior predictive check for model m0")
)

# Building model
ACI_m0 <- brm(
  formula = ACI_f0,
  data = d,
  family = gaussian,
  prior = ACI_p0,
  #file = "ACI_m0_prior",
  sample_prior = T,
  backend = "cmdstanr"
  #threads = threading(2)
)

# Visualizing the priors
prior_samples(ACI_m0) %>% 

## Drawing out possible predictions from the priors
  mutate(b = b_Diagnosis2 - b_Diagnosis1) %>% 
  slice_sample(n = 50) %>%
  rownames_to_column("draw") %>%
  expand(nesting(draw, b),
         a = c(-2, 2)) %>%
  mutate(d = b * a) %>% 

## Plotting the lines based on the priors
  ggplot(aes(x = a, y = d)) +
  geom_line(aes(group = draw),
            color = "firebrick", alpha = .4) +
  labs(x = "Change in Experimental Group",
       y = "Altercentric Intrusion (std)") +
  coord_cartesian(ylim = c(-2, 2)) +
  theme_bw() +
  theme(panel.grid = element_blank()) +
  ggtitle("Possible slopes based on priors beta = normal(0, 1) & sigma = normal(1, 0.5)") 


```


```{r}
# Work on m1
ACI_p1 <- c(
  prior(normal(0, 0.5), class = b, coef = Diagnosis1),
  prior(normal(0, 0.5), class = b, coef = Diagnosis2),
  prior(normal(1, 0.5), class = sigma))

# Building prior model
ACI_m1_prior <- brm(
  formula = ACI_f0,
  data = d,
  family = gaussian,
  prior = ACI_p1,
  #file = "ACI_m1_prior",
  sample_prior = "only",
  backend = "cmdstanr"
  #threads = threading(2)
)

# PP Check
(
  p1_m1 <- pp_check(ACI_m1_prior, nsamples = 100) +
    xlab("Altercentric Intrusion (std)") +
    ylab("Density") +
    ggtitle("Prior predictive check for model m1")
)

p1_m0 + p1_m1

# Building model
(
  ACI_m1 <- brm(
    formula = ACI_f0,
    data = d,
    family = gaussian,
    prior = ACI_p1,
    #file = "ACI_m1",
    sample_prior = T,
    backend = "cmdstanr"
    #threads = threading(2)
  )
)

# Visualizing the priors
prior_samples(ACI_m1) %>% 

## Drawing out possible predictions from the priors
  mutate(b = b_Diagnosis2 - b_Diagnosis1) %>% 
  slice_sample(n = 50) %>%
  rownames_to_column("draw") %>%
  expand(nesting(draw, b),
         a = c(-2, 2)) %>%
  mutate(d = b * a) %>% 

## Plotting the lines based on the priors
  ggplot(aes(x = a, y = d)) +
  geom_line(aes(group = draw),
            color = "firebrick", alpha = .4) +
  labs(x = "Change in Experimental Group",
       y = "Altercentric Intrusion (std)") +
  coord_cartesian(ylim = c(-2, 2)) +
  theme_bw() +
  theme(panel.grid = element_blank()) +
  ggtitle("Possible slopes based on priors beta = normal(0, 0.5) & sigma = normal(1, 0.5)")

# Posterior predictive check
p2_m1 <- pp_check(ACI_m1, nsamples = 100) +
  xlab("Altercentric Intrusion (std)") +
  ylab("Density") +
  ggtitle("Posterior predictive check for model m1")

p1_m1 + p2_m1


# Sampling from the posterior
posterior_m1 <- posterior_samples(ACI_m1)  %>% 
  mutate(diff = b_Diagnosis2 - b_Diagnosis1)

# Creating a long format of the posterior to plot the different distributions together
posterior_m1 %>% 
  pivot_longer(c(b_Diagnosis1, b_Diagnosis2, prior_b_Diagnosis1), names_to = "Distributions") %>% 
  ggplot(aes(fill = Distributions)) +

# Plotting the prior and posterior distributions
  geom_density(aes(value), alpha=0.3) + 
  theme_minimal()+
  ggtitle("Posterior beta distributions for both groups plotted against the prior") + 
  scale_fill_discrete(name = "Distributions", labels = c("Control", "Schizophrenic", "Prior")) +
  xlab("Altercentric Intrusion (std)")

## Plotting the difference
posterior_m1 %>% ggplot() +
  geom_density(aes(diff), fill = "blue", alpha=0.3) + 
  theme_minimal() + 
  ggtitle("Distribution of difference in beta for control and schizophrenic patients")

# slicing the posterior
posterior_slice <- posterior_m1 %>% 
  slice(1:100)

# plotting model implications
d %>% 
  ggplot(aes(x = Diagnosis, y = ACI)) +
  geom_abline(intercept = posterior_slice[ ,1] - (posterior_slice[ ,2] - posterior_slice[ ,1]), 
              slope     = posterior_slice[ ,2] - posterior_slice[ ,1], alpha = 0.1) +
  geom_point(shape = 1, size = 2, color = "royalblue") +
  theme_minimal() +
  ggtitle("Model predictions plotted against scaled data, N = 100") +
  scale_x_discrete(labels=c("1" = "Control", "2" = "Schizophrenia")) + 
  ylab("Altercentric Intrusion (std)")

# testing the hypotheses
hypothesis(ACI_m1, "Diagnosis1 = Diagnosis2")
hypothesis(ACI_m1, "Diagnosis1 > Diagnosis2")
hypothesis(ACI_m1, "Diagnosis1 < Diagnosis2")

```

Q1.2) Is altercentric intrusion related to specific symptoms *in the patients*? Identify which of the symptoms could be relevant (given their description above). Should you include more than one symptom? Build models, priors, predictive checks. Assess the evidence and report models and results, including plots. Discuss whether the results make sense.

```{r}
# Defining functions for pairs-plot
reg <- function(x, y, col) abline(lm(y ~ x), col = col)

panel.lm <-
  function (x, y, col = par("col"), bg = NA, pch = par("pch"), 
            cex = 1, col.smooth = "red", span = 2 / 3, iter = 3, ...)  {
    points(x, y, pch = pch, col = col, bg = bg, cex = cex)
    ok <- is.finite(x) & is.finite(y)
    if (any(ok)) 
      reg(x[ok], y[ok], col.smooth)
  }

panel.cor <- function(x, y, digits = 2, prefix = "", cex.cor, ...) {
  usr <- par("usr")
  on.exit(par(usr))
  par(usr = c(0, 1, 0, 1))
  r <- cor(x, y)
  txt <- format(c(r, 0.123456789), digits = digits)[1]
  txt <- paste0(prefix, txt)
  text(0.5, 0.5, txt, cex = 1.1, font = 4)
}
```

```{r}
# subsetting only the schizophrenic group
d_sub <- d %>% filter(Diagnosis == 2)

# Pairs-plot for everybody
pairs( ~ ACI + MR + APA + VH + Diagnosis, data = d,
  panel = panel.lm,
  cex = 1.5,
  pch = 19,
  col = adjustcolor(4, .4),
  cex.labels = 2,
  font.labels = 2,
  lower.panel = panel.cor
)

# pairs-plot for only the schizophrenic group
pairs( ~ ACI + MR + APA + VH, data = d_sub,
  panel = panel.lm,
  cex = 1.5,
  pch = 19,
  col = adjustcolor(4, .4),
  cex.labels = 2,
  font.labels = 2,
  lower.panel = panel.cor
)

cor.test(d_sub$MindReading, d_sub$VoiceHearing)

```


### Apathy

```{r}
## Creating model with each predictor to see how much they explain

# Voicehearing
ModelAPA <- bf(ACI ~ 0 + APA)

prior_defAPA <- c(prior(normal(1,0.5), class = sigma),
  prior(normal(0,0.5), class = b))

# Specifiying a model for assessing the priors
model_priorAPA <- brm(
  formula = ModelAPA,
  data = d_sub,
  family = gaussian,
  prior = prior_defAPA,
  sample_prior="only",
  file = "model_prior",
  backend="cmdstanr",
  threads = threading(2)
)

# Checking priors using ppcheck (prior predictive check)
pp_check(model_priorAPA, nsamples = 100)

# Creating the model
modelAPA <- brm(
  formula = ModelAPA,
  data = d_sub,
  family = gaussian,
  prior = prior_defAPA,
  sample_prior=T,
  backend="cmdstanr",
  threads = threading(2)
)

# Posterior predictive check
pp_check(modelAPA, nsamples = 100)

print(modelAPA)

```

### Voicehearing
```{r}

## Creating model with each predictor to see how much they explain

# Voicehearing
ModelVH <- bf(ACI ~ 0 + VH)

prior_defVH <- c(prior(normal(1,0.5), class = sigma),
  prior(normal(0,0.5), class = b))

# Specifiying a model for assessing the priors
model_priorVH <- brm(
  formula = ModelVH,
  data = d_sub,
  family = gaussian,
  prior = prior_defVH,
  sample_prior="only",
  file = "model_prior",
  backend="cmdstanr",
  threads = threading(2)
)

# Checking priors using ppcheck (prior predictive check)
pp_check(model_priorVH, nsamples = 100)

# Creating the model
modelVH <- brm(
  formula = ModelVH,
  data = d_sub,
  family = gaussian,
  prior = prior_defVH,
  sample_prior=T,
  backend="cmdstanr",
  threads = threading(2)
)


# Posterior predictive check
pp_check(modelVH, nsamples = 100)

print(modelVH)

```
### Mindreading
```{r}
# Mindreading

ModelMR <- bf(ACI ~ 0 + MR)

prior_defMR <- c(prior(normal(1,0.5), class = sigma),
  prior(normal(0,0.5), class = b))

# Specifiying a model for assessing the priors
model_priorMR <- brm(
  formula = ModelMR,
  data = d_sub,
  family = gaussian,
  prior = prior_defMR,
  sample_prior="only",
  file = "model_prior",
  backend="cmdstanr",
  threads = threading(2)
)

# Checking priors using ppcheck (prior predictive check)
pp_check(model_priorMR, nsamples = 100)

# Creating the model
modelMR <- brm(
  formula = ModelMR,
  data = d_sub,
  family = gaussian,
  prior = prior_defMR,
  sample_prior=T,
  backend="cmdstanr",
  threads = threading(2)
)

# Posterior predictive check
pp_check(modelMR, nsamples = 100)

print(modelMR)

```

Two predictors included
```{r}
# Specifying model
ModelTwo <- bf(ACI ~ 0 + MR + VH)

# Using get prior
get_prior(ModelTwo,  d_sub, family = gaussian)

# Defining priors
prior_mTwo <- c(
  prior(normal(1,0.5), class = sigma),
  prior(normal(0,0.5), class = b)
)

# Specifiying a model for assessing the priors
model_mTwo_prior <- brm(
  formula = ModelTwo,
  data = d_sub,
  family = gaussian,
  prior = prior_mTwo,
  sample_prior="only",
  #file = "model_prior",
  backend="cmdstanr",
  threads = threading(2)
)

# Checking priors using ppcheck (prior predictive check)
pp_check(model_mTwo_prior, nsamples = 100)

# Creating the model
model_mTwo <- brm(
  formula = ModelTwo,
  data = d_sub,
  family = gaussian,
  prior = prior_mTwo,
  sample_prior = T,
  backend = "cmdstanr",
  threads = threading(2)
)

# Posterior predictive check
pp_check(model_mTwo, nsamples = 100)

# Sampling from the posterior
posterior_samples(model_mTwo) %>% 

# Creating a long format of the posterior to plot the different distributions together
  pivot_longer(c(b_MR, b_VH, prior_b), names_to = "Estimates") %>%

# Plotting the prior and posterior distributions
  ggplot(aes(fill = Estimates)) +
  geom_density(aes(value), alpha = 0.3) +
  theme_minimal() +
  scale_fill_discrete(name = "Estimates", labels = c("MR", "VH", "Prior")) +
  xlab("Altercentric Intrusion (std)")

pairs(model_mTwo)

print(model_mTwo)

```

All predictors included
```{r}
# Specifying model
Model4 <- bf(ACI ~ 0 + MR + VH + APA)

# Using get prior
get_prior(Model4,  d_sub, family = gaussian)

# Defining priors
prior_def4 <- c(
  prior(normal(1,0.5), class = sigma),
  prior(normal(0,0.5), class = b)
)

# Specifiying a model for assessing the priors
model_prior4 <- brm(
  formula = Model4,
  data = d_sub,
  family = gaussian,
  prior = prior_def4,
  sample_prior="only",
  file = "model_prior",
  backend="cmdstanr",
  threads = threading(2)
)

# Checking priors using ppcheck (prior predictive check)
pp_check(model_prior4, nsamples = 100)


# Creating the model
model4 <- brm(
  formula = Model4,
  data = d_sub,
  family = gaussian,
  prior = prior_def4,
  sample_prior=T,
  backend="cmdstanr",
  threads = threading(2)
)

# Posterior predictive check
pp_check(model4, nsamples = 100)

# Sampling from the posterior
posterior_samples(model4) %>% 

# Creating a long format of the posterior to plot the different distributions together
  pivot_longer(c(b_MR, b_VH, b_APA, prior_b), names_to = "Estimates") %>%
  
# Plotting the prior and posterior distributions
  ggplot(aes(fill = Estimates)) +
  geom_density(aes(value), alpha = 0.3) +
  theme_minimal() +
  scale_fill_discrete(name = "Estimates", labels = c("APA", "MR", "VH", "Prior")) +
  xlab("Altercentric Intrusion (std)")

pairs(model4)

print(model4)

```

(PART 2)
#We investigate the effect of conditioning only on the schizophrenic population, and thereby introducing a collider bias. We do this using rethinking::quap() because this allows us to make a coefficient plot and easily compare the models and effects.
```{r}
#We only want to look at the patients (Diagnosis = 2)
data_quap <- d #Copying the data for cooperation purposes
d2 <- d_sub #Only schizophrenic

#Remaking the models with quap - including both neurotypicals and schrizophrenic population:

#Model with Mindreading
m_MR_full <- quap(
alist(
ACI_scale ~ dnorm( mu , sigma ) ,
mu <- a[Diagnosis] + b_MR * MR_scale,
a[Diagnosis] ~ dnorm( 0 , 0.2 ) , #prior 
b_MR ~ dnorm( 0 , 0.5 ) ,
sigma ~ dnorm(1, 0.5)
) , data = data_quap )

precis( m_MR_full , depth = 2)


#Model with Apathy
m_APA_full <- quap(
alist(
ACI_scale ~ dnorm( mu , sigma ) ,
mu <- a[Diagnosis] + b_Apath * Apath_scale,
a[Diagnosis] ~ dnorm( 0 , 0.2 ) ,
b_Apath ~ dnorm( 0 , 0.5 ) ,
sigma ~ dnorm(1, 0.5)
) , data = data_quap )

precis(m_APA_full, depth = 2) 

#Model with voice hearing
m_VH_full <- quap(
alist(
ACI_scale ~ dnorm( mu , sigma ) ,
mu <- a[Diagnosis] + b_VH * VH_scale,
a[Diagnosis] ~ dnorm( 0 , 0.2 ) ,
b_VH ~ dnorm( 0 , 0.5 ) ,
sigma ~ dnorm(1, 0.5)
) , data = data_quap )

precis(m_VH_full, depth = 2)

#Model with voice hearing + Mindreading
m_VH_MR_full <- quap(
alist(
ACI_scale ~ dnorm( mu , sigma ) ,
mu <- a[Diagnosis] + b_VH * VH_scale + b_MR * MR_scale,
a[Diagnosis] ~ dnorm( 0 , 0.2 ) ,
b_VH ~ dnorm( 0 , 0.5 ) ,
b_MR ~ dnorm(0, 0.5),
sigma ~ dnorm(1, 0.5)
) , data = data_quap )

precis(m_VH_MR_full, depth = 2)

#Model including all predictors
m_ALL_full <- quap(
alist(
ACI_scale ~ dnorm( mu , sigma ) ,
mu <- a[Diagnosis] + b_VH * VH_scale + b_MR * MR_scale + b_Apath * Apath_scale,
a[Diagnosis] ~ dnorm( 0 , 0.2 ) ,
b_VH ~ dnorm( 0 , 0.5 ) ,
b_MR ~ dnorm(0, 0.5),
b_Apath ~ dnorm(0, 0.5),
sigma ~ dnorm(1, 0.5)
) , data = data_quap )

precis(m_ALL_full, depth = 2)


#Here we make the models only with the schizophrenic population:

#Model with Mindreading
m_MR_schz <- quap(
alist(
ACI_scale ~ dnorm( mu , sigma ) ,
mu <- b_MR * MR_scale,
#a ~ dnorm( 0 , 0.2 ) , #No intercept when we only have one level of diagnosis
b_MR ~ dnorm( 0 , 0.5 ) ,
sigma ~ dnorm(1, 0.5)
) , data = d2 )

precis( m_MR_schz )


#Model with apathy - not gonna do this with brms because..
m_APA_schz <- quap(
alist(
ACI_scale ~ dnorm( mu , sigma ) ,
mu <- b_Apath * Apath_scale,
#a ~ dnorm( 0 , 0.2 ) ,
b_Apath ~ dnorm( 0 , 0.5 ) ,
sigma ~ dnorm(1, 0.5)
) , data = d2 )

precis(m_APA_schz)

#Model with voice hearing
m_VH_schz <- quap(
alist(
ACI_scale ~ dnorm( mu , sigma ) ,
mu <- b_VH * VH_scale,
#a ~ dnorm( 0 , 0.2 ) ,
b_VH ~ dnorm( 0 , 0.5 ) ,
sigma ~ dnorm(1, 0.5)
) , data = d2 )

precis(m_VH_schz)


#Model with voice hearing
m_VH_MR_schz <- quap(
alist(
ACI_scale ~ dnorm( mu , sigma ) ,
mu <- b_VH * VH_scale + b_MR * MR_scale,
#a ~ dnorm( 0 , 0.2 ) ,
b_VH ~ dnorm( 0 , 0.5 ) ,
b_MR ~ dnorm(0, 0.5),
sigma ~ dnorm(1, 0.5)
) , data = d2 )

precis(m_VH_MR_schz)

#Model with all predictors:
m_ALL_schz <- quap(
alist(
ACI_scale ~ dnorm( mu , sigma ) ,
mu <- b_VH * VH_scale + b_MR * MR_scale + b_Apath * Apath_scale,
#a ~ dnorm( 0 , 0.2 ) , #
b_VH ~ dnorm( 0 , 0.5 ) ,
b_MR ~ dnorm(0, 0.5),
b_Apath ~ dnorm(0, 0.5),
sigma ~ dnorm(1, 0.5)
) , data = d2 )

precis(m_ALL_schz)

#Plotting model coefficients:
plot(coeftab(m_APA_full, m_MR_full, m_VH_full, m_VH_MR_full, m_ALL_full), par=c("b_VH","b_MR", "b_Apath"))

#And for the schizophrenic population
plot(coeftab(m_APA_schz, m_MR_schz, m_VH_schz, m_VH_MR_schz, m_ALL_schz), par=c("b_VH","b_MR", "b_Apath"))

#Potential plotting issues can be fixed by:
#setMethod( "plot" , "coeftab" , function(x,y,...) coeftab_plot(x,y,...) )
#getMethod("plot", "coeftab")
```


