---
title: "Understanding what the heck is going on"
author: "Klara Krøyer Fomsgaard"
date: "3/4/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Load data & packages
```{r}
pacman::p_load(tidyverse,brms,rethinking, tidybayes)

data <- read_csv("Ass2.csv")
```

#### Scaling, removing outliers and converting diagnosis into index variable
```{r}

# Scale altercentric intrusion to make it easier to work with
data$ACI_scale <- scale(data$AltercentricIntrusion)

# Converting Diagnosis into an index, to have the same amount of uncertainty for both groups, and changing it to factor
data <-
  data %>% 
  mutate(Diagnosis = ifelse(Diagnosis == 1, 2, 1)) %>% 
  mutate(Diagnosis = factor(Diagnosis))

```

#### Plot the scaled data
```{r}
# Density plot
dens(data$ACI_scale)

# Boxplot
ggplot(data, aes(x = Diagnosis, y = ACI_scale))+
  geom_boxplot(aes(group = Diagnosis, fill = Diagnosis, alpha = .5))+
  theme_minimal()

```
### Making the model

ACI_i ~ Normal(mu_i,SD)
mu_i = alpha + beta*D_i
alpha ~ Normal(0,0.2)
beta ~ Normal(0,0.5) 
SD ~ Exponential(1)

##### Why are we choosing this model with these priors?

The likehood is believed to be a normal distribution with a mean and sd, where the mean is given by a linear regression mu_i = alpha + beta*D_i.
The alpha is set to be a normal distribution with mean 0 and sd 0.2. For the beta, the mean is 0 and the sd 0.5. Mean is 0 because the data is standardized, and we wish to let the data tell us the distribution of effect sizes. As we don't know much about what we expect to see, we start out with some more vague priors.

```{r}

# Specifying model
Model <- bf(ACI_scale ~ 0 + Diagnosis)

# Using get prior
get_prior(Model,  data, family = gaussian)

# Defining priors
prior_def <- c(
  prior(normal(1,0.5), class = sigma),
  prior(normal(0,0.5), class = b)
)

# Specifiying a model for assessing the priors
model_prior <- brm(
  formula = Model,
  data = data,
  family = gaussian,
  prior = prior_def,
  sample_prior="only",
  file = "model_prior",
  backend="cmdstanr",
  threads = threading(2)
)

# Checking priors using ppcheck (prior predictive check)
pp_check(model_prior, nsamples = 100)

# Creating the model
model <- brm(
  formula = Model,
  data = data,
  family = gaussian,
  prior = prior_def,
  sample_prior=T,
  backend="cmdstanr",
  threads = threading(2)
)

# Visualizing the priors
prior <- prior_samples(model)
prior %>% glimpse()

## Drawing out possible predictions from the priors
prior %>% 
  slice_sample(n = 50) %>% 
  rownames_to_column("draw") %>% 
  expand(nesting(draw, b),
         a = c(-2, 2)) %>% 
  mutate(d = b * a) %>% 

## Plotting the lines based on the priors
ggplot(aes(x = a, y = d)) +
  geom_line(aes(group = draw),
            color = "firebrick", alpha = .4) +
  labs(x = "Diagnosis (std)",
       y = "ALtercentric intrusion (std)") +
  coord_cartesian(ylim = c(-2, 2)) +
  theme_bw() +
  theme(panel.grid = element_blank()) +
  ggtitle("Possible slopes based on priors beta = normal(0,0.5) & sigma = normal(1,0.5)")

```
```{r}

# Posterior predictive check
pp_check(model, nsamples = 100)

# Sampling from the posterior
posterior <- posterior_samples(model)

# Creating a long format of the posterior to plot the different distributions together
posterior_long <- posterior %>% 
  pivot_longer(c(b_Diagnosis1,b_Diagnosis2,prior_b), names_to = "Distributions")

## plotting the individual posterior distributions against their priors
### Sigma
ggplot(posterior) +
  theme_classic() +
  geom_density(aes(prior_sigma), fill="red", alpha=0.3) +
  geom_density(aes(sigma), fill="blue", alpha=0.5)

### Control
ggplot(posterior) +
  theme_minimal() +
  geom_density(aes(prior_b), fill="red", alpha=0.3) +
  geom_density(aes(b_Diagnosis1), fill="blue", alpha=0.5)

### Schizophrenic patients
ggplot(posterior) +
  theme_minimal() +
  geom_density(aes(prior_b), fill="red", alpha=0.3) +
  geom_density(aes(b_Diagnosis2), fill="blue", alpha=0.5)

## Plotting both groups against the prior
ggplot(posterior_long, aes(fill = Distributions)) +
  geom_density(aes(value), alpha=0.3) + 
  theme_minimal()+
  ggtitle("Posterior beta distributions for both groups plotted against the prior")

# Extracting mean and sd fro both groups   ???? Is this correct?
mean(posterior$b_Diagnosis1)
sd(posterior$b_Diagnosis1)

mean(posterior$b_Diagnosis2)
sd(posterior$b_Diagnosis2)


# Calculating the difference between the two groups i.e. the slope, and the interval of how the slope is most likely to look
posterior_samples(model) %>% 
  mutate(diff_fm = b_Diagnosis2 - b_Diagnosis1) %>% 
  gather(key, value, -`lp__`) %>% 
  group_by(key) %>% 
  mean_qi(value, .width = .89)

# making a separate column for the difference in the posterior
posterior <- posterior %>% 
  mutate(diff = b_Diagnosis2 - b_Diagnosis1)

## Plotting the difference
ggplot(posterior) +
  geom_density(aes(diff), fill = "blue", alpha=0.3) + 
  theme_minimal() + 
  ggtitle("Distribution of difference in beta for control and schizophrenic patients")

# Plotting model predictions against the data 

## Subsets the data to 100 predictions
posterior_slice <- posterior %>% 
  slice(1:100)

data %>% 
  ggplot(aes(x = Diagnosis, y = ACI_scale)) +
  geom_abline(intercept = posterior_slice[ ,1], 
              slope     = posterior_slice[ ,2], alpha = 0.1) +
  geom_point(shape = 1, size = 2, color = "royalblue") +
  theme_minimal() +
  ggtitle("Model predictions plotted against scaled data, N = 100") +
  scale_x_discrete(labels=c("1" = "Control", "2" = "Schizophrenia"))
```
## Question 2
Given that altercentric intrusion is when the patient has trouble filtering out the perspective of other people, "mindreading" may be a symptom related to this phenomena. Potentially "voice-hearing" could be a symptom too, as it might interfere with the perspective of the patient in the task. Apathy might not be a relevant symptom for this investigation

ACI_i ~ Normal(mu_i,SD)
mu_i = beta1 * VH_i + beta2 * MR_i
beta1 ~ Normal(0,0.5)
beta2 ~ Normal(0,0.5)
sigma ~ Normal(1, 0.5)

```{r}
## Scaling variables
data$VH_scale <- scale(data$VoiceHearing)
data$MR_scale <- scale(data$MindReading)
data$APA_scale <- scale(data$Apathy)


# Subsetting the data to include only patients with schizophrenia

data_2 <- data %>% 
  subset(Diagnosis == 2)


```

### Apathy

```{r}
## Creating model with each predictor to see how much they explain

# Voicehearing
ModelAPA <- bf(ACI_scale ~ 0 + APA_scale)

prior_defAPA <- c(prior(normal(1,0.5), class = sigma),
  prior(normal(0,0.5), class = b))

# Specifiying a model for assessing the priors
model_priorAPA <- brm(
  formula = ModelAPA,
  data = data_2,
  family = gaussian,
  prior = prior_defAPA,
  sample_prior="only",
  file = "model_prior",
  backend="cmdstanr",
  threads = threading(2)
)

# Checking priors using ppcheck (prior predictive check)
pp_check(model_priorAPA, nsamples = 100)

# Creating the model
modelAPA <- brm(
  formula = ModelAPA,
  data = data_2,
  family = gaussian,
  prior = prior_defAPA,
  sample_prior=T,
  backend="cmdstanr",
  threads = threading(2)
)

# Visualizing the priors
priorAPA <- prior_samples(modelAPA)
priorAPA %>% glimpse()

## Drawing out possible predictions from the priors
priorAPA %>% 
  slice_sample(n = 50) %>% 
  rownames_to_column("draw") %>% 
  expand(nesting(draw, b),
         a = c(-2, 2)) %>% 
  mutate(d = b * a) %>% 

## Plotting the lines based on the priors
ggplot(aes(x = a, y = d)) +
  geom_line(aes(group = draw),
            color = "firebrick", alpha = .4) +
  labs(x = "Diagnosis (std)",
       y = "Altercentric intrusion (std)") +
  coord_cartesian(ylim = c(-2, 2)) +
  theme_bw() +
  theme(panel.grid = element_blank()) 

# Posterior predictive check
pp_check(modelAPA, nsamples = 100)

# Sampling from the posterior
posteriorAPA <- posterior_samples(modelAPA)

mean(posteriorAPA$b_APA_scale)
sd(posteriorAPA$b_APA_scale)

ggplot(posteriorAPA) +
  geom_density(aes(b_APA_scale), fill="blue", alpha=0.2) +
  theme_minimal()

print(modelAPA)


hypothesis(modelAPA, c("APA_scale > 0","APA_scale < 0","APA_scale = 0"))
```

### Voicehearing
```{r}

## Creating model with each predictor to see how much they explain

# Voicehearing
ModelVH <- bf(ACI_scale ~ 0 + VH_scale)

prior_defVH <- c(prior(normal(1,0.5), class = sigma),
  prior(normal(0,0.5), class = b))

# Specifiying a model for assessing the priors
model_priorVH <- brm(
  formula = ModelVH,
  data = data_2,
  family = gaussian,
  prior = prior_defVH,
  sample_prior="only",
  file = "model_prior",
  backend="cmdstanr",
  threads = threading(2)
)

# Checking priors using ppcheck (prior predictive check)
pp_check(model_priorVH, nsamples = 100)

# Creating the model
modelVH <- brm(
  formula = ModelVH,
  data = data_2,
  family = gaussian,
  prior = prior_defVH,
  sample_prior=T,
  backend="cmdstanr",
  threads = threading(2)
)

# Visualizing the priors
priorVH <- prior_samples(modelVH)
priorVH %>% glimpse()

## Drawing out possible predictions from the priors
priorVH %>% 
  slice_sample(n = 50) %>% 
  rownames_to_column("draw") %>% 
  expand(nesting(draw, b),
         a = c(-2, 2)) %>% 
  mutate(d = b * a) %>% 

## Plotting the lines based on the priors
ggplot(aes(x = a, y = d)) +
  geom_line(aes(group = draw),
            color = "firebrick", alpha = .4) +
  labs(x = "Diagnosis (std)",
       y = "Altercentric intrusion (std)") +
  coord_cartesian(ylim = c(-2, 2)) +
  theme_bw() +
  theme(panel.grid = element_blank()) 

# Posterior predictive check
pp_check(modelVH, nsamples = 100)

# Sampling from the posterior
posteriorVH <- posterior_samples(modelVH)

mean(posteriorVH$b_VH_scale)
sd(posteriorVH$b_VH_scale)

ggplot(posteriorVH) +
  geom_density(aes(b_VH_scale), fill="blue", alpha=0.2) +
  theme_minimal()

print(modelVH)

hypothesis(modelVH, c("VH_scale > 0","VH_scale < 0","VH_scale = 0"))
```
### Mindreading
```{r}
# Mindreading

ModelMR <- bf(ACI_scale ~ 0 + MR_scale)

prior_defMR <- c(prior(normal(1,0.5), class = sigma),
  prior(normal(0,0.5), class = b))

# Specifiying a model for assessing the priors
model_priorMR <- brm(
  formula = ModelMR,
  data = data_2,
  family = gaussian,
  prior = prior_defMR,
  sample_prior="only",
  file = "model_prior",
  backend="cmdstanr",
  threads = threading(2)
)

# Checking priors using ppcheck (prior predictive check)
pp_check(model_priorMR, nsamples = 100)

# Creating the model
modelMR <- brm(
  formula = ModelMR,
  data = data_2,
  family = gaussian,
  prior = prior_defMR,
  sample_prior=T,
  backend="cmdstanr",
  threads = threading(2)
)

# Visualizing the priors
priorMR <- prior_samples(modelMR)
priorMR %>% glimpse()

## Drawing out possible predictions from the priors
priorMR %>% 
  slice_sample(n = 50) %>% 
  rownames_to_column("draw") %>% 
  expand(nesting(draw, b),
         a = c(-2, 2)) %>% 
  mutate(d = b * a) %>% 

## Plotting the lines based on the priors
ggplot(aes(x = a, y = d)) +
  geom_line(aes(group = draw),
            color = "firebrick", alpha = .4) +
  labs(x = "Diagnosis (std)",
       y = "Altercentric intrusion (std)") +
  coord_cartesian(ylim = c(-2, 2)) +
  theme_bw() +
  theme(panel.grid = element_blank()) 

# Posterior predictive check
pp_check(modelMR, nsamples = 100)

# Sampling from the posterior
posteriorMR <- posterior_samples(modelMR)

mean(posteriorMR$b_MR_scale)
sd(posteriorMR$b_MR_scale)

ggplot(posteriorMR) +
  geom_density(aes(b_MR_scale), fill="blue", alpha=0.2) +
  theme_minimal()

print(modelMR)

hypothesis(modelMR, c("MR_scale > 0","MR_scale < 0","MR_scale = 0"))

```

Both predictors included
```{r}
# Specifying model
Model4 <- bf(ACI_scale ~ 0 + VH_scale + MR_scale)

# Using get prior
get_prior(Model4,  data_2, family = gaussian)

# Defining priors
prior_def4 <- c(
  prior(normal(1,0.5), class = sigma),
  prior(normal(0,0.5), class = b)
)

# Specifiying a model for assessing the priors
model_prior4 <- brm(
  formula = Model4,
  data = data_2,
  family = gaussian,
  prior = prior_def4,
  sample_prior="only",
  file = "model_prior",
  backend="cmdstanr",
  threads = threading(2)
)

# Checking priors using ppcheck (prior predictive check)
pp_check(model_prior4, nsamples = 100)


# Creating the model
model4 <- brm(
  formula = Model4,
  data = data_2,
  family = gaussian,
  prior = prior_def4,
  sample_prior=T,
  backend="cmdstanr",
  threads = threading(2)
)

# Visualizing the priors
prior4 <- prior_samples(model4)
prior4 %>% glimpse()

## Drawing out possible predictions from the priors
prior4 %>% 
  slice_sample(n = 50) %>% 
  rownames_to_column("draw") %>% 
  expand(nesting(draw, b),
         a = c(-2, 2)) %>% 
  mutate(d = b * a) %>% 

## Plotting the lines based on the priors
ggplot(aes(x = a, y = d)) +
  geom_line(aes(group = draw),
            color = "firebrick", alpha = .4) +
  labs(x = "Diagnosis (std)",
       y = "ALtercentric intrusion (std)") +
  coord_cartesian(ylim = c(-2, 2)) +
  theme_bw() +
  theme(panel.grid = element_blank()) 

# Posterior predictive check
pp_check(model4, nsamples = 100)

# Sampling from the posterior
posterior4 <- posterior_samples(model4)

pairs(model4)

ggplot(posterior4) +
  geom_density(aes(b_MR_scale), fill="blue", alpha=0.2)+
  geom_density(aes(b_VH_scale), fill = "red", alpha = 0.2)+
  geom_density(aes(prior_b), fill = "grey", alpha = 0.2)+
  theme_minimal()+
  ggtitle("Posterior predictive distribution: ACI ~ 0 + Mindreading + VoiceHearing")

print(model4)


```
```{r}
# Specifying model
Model5 <- bf(ACI_scale ~ 0 + VH_scale + MR_scale + APA_scale)

# Using get prior
get_prior(Model5,  data_2, family = gaussian)

# Defining priors
prior_def5 <- c(
  prior(normal(1,0.5), class = sigma),
  prior(normal(0,0.5), class = b)
)

# Specifiying a model for assessing the priors
model_prior5 <- brm(
  formula = Model5,
  data = data_2,
  family = gaussian,
  prior = prior_def5,
  sample_prior="only",
  file = "model_prior",
  backend="cmdstanr",
  threads = threading(2)
)

# Checking priors using ppcheck (prior predictive check)
pp_check(model_prior5, nsamples = 100)


# Creating the model
model5 <- brm(
  formula = Model5,
  data = data_2,
  family = gaussian,
  prior = prior_def5,
  sample_prior=T,
  backend="cmdstanr",
  threads = threading(2)
)

# Visualizing the priors
prior5 <- prior_samples(model5)
prior5 %>% glimpse()

## Drawing out possible predictions from the priors
prior5 %>% 
  slice_sample(n = 50) %>% 
  rownames_to_column("draw") %>% 
  expand(nesting(draw, b),
         a = c(-2, 2)) %>% 
  mutate(d = b * a) %>% 

## Plotting the lines based on the priors
ggplot(aes(x = a, y = d)) +
  geom_line(aes(group = draw),
            color = "firebrick", alpha = .5) +
  labs(x = "Diagnosis (std)",
       y = "ALtercentric intrusion (std)") +
  coord_cartesian(ylim = c(-2, 2)) +
  theme_bw() +
  theme(panel.grid = element_blank()) 

# Posterior predictive check
pp_check(model5, nsamples = 100)

# Sampling from the posterior
posterior5 <- posterior_samples(model5)

pairs(model5)

ggplot(posterior5) +
  geom_density(aes(b_MR_scale), fill="blue", alpha=0.2)+
  geom_density(aes(b_VH_scale), fill = "red", alpha = 0.2)+
  geom_density(aes(b_APA_scale), fill = "green", alpha = 0.2)+
  geom_density(aes(prior_b), fill = "grey", alpha = 0.2)+
  theme_minimal() +
  ggtitle("Posterior predictive destributions: ACI ~ 0 + Mindreading + VoiceHearing + Apathy")

print(model5)
```

## Second part

### Q2.1) 
However, we know that the diagnosis is based on symptom assessment: if the overall sum of symptoms is severe enough, the participant gets a diagnosis. In other words, by selecting the patients, and including the symptoms in the model we might have inadvertently introduced an issue in our inference. Do try to draw a causal graph (Directed Acyclical Graph) of the variables and compare it with the types of causal graphs presented in the slides. Discuss which biases you might have introduced.

### Q2.2.) 
Redesign your analysis following the graph and report how the results change
```{r}
# Specifying model
Model6 <- bf(ACI_scale ~ 0 + VH_scale + MR_scale)

# Using get prior
get_prior(Model6,  data, family = gaussian)

# Defining priors
prior_def6 <- c(
  prior(normal(1,0.5), class = sigma),
  prior(normal(0,0.5), class = b)
)

# Specifiying a model for assessing the priors
model_prior6 <- brm(
  formula = Model6,
  data = data,
  family = gaussian,
  prior = prior_def6,
  sample_prior="only",
  file = "model_prior",
  backend="cmdstanr",
  threads = threading(2)
)

# Checking priors using ppcheck (prior predictive check)
pp_check(model_prior6, nsamples = 100)


# Creating the model
model6 <- brm(
  formula = Model6,
  data = data,
  family = gaussian,
  prior = prior_def6,
  sample_prior=T,
  backend="cmdstanr",
  threads = threading(2)
)

# Visualizing the priors
prior6 <- prior_samples(model6)
prior6 %>% glimpse()

## Drawing out possible predictions from the priors
prior6 %>% 
  slice_sample(n = 50) %>% 
  rownames_to_column("draw") %>% 
  expand(nesting(draw, b),
         a = c(-2, 2)) %>% 
  mutate(d = b * a) %>% 

## Plotting the lines based on the priors
ggplot(aes(x = a, y = d)) +
  geom_line(aes(group = draw),
            color = "firebrick", alpha = .4) +
  labs(x = "Diagnosis (std)",
       y = "ALtercentric intrusion (std)") +
  coord_cartesian(ylim = c(-2, 2)) +
  theme_bw() +
  theme(panel.grid = element_blank()) 

# Posterior predictive check
pp_check(model6, nsamples = 100)

¨# Sampling from the posterior
posterior6 <- posterior_samples(model6)

pairs(model6)

ggplot(posterior6) +
  geom_density(aes(b_MR_scale), fill="blue", alpha=0.2)+
  geom_density(aes(b_VH_scale), fill = "red", alpha = 0.2)+
  geom_density(aes(prior_b), fill = "grey", alpha = 0.2)+
  theme_minimal()+
  ggtitle("ACI ~ 0 + Mindreading + VoiceHearing, All participants")

print(model6)

hypothesis(model6, c("MR_scale > 0","MR_scale < 0","MR_scale = 0", "VH_scale > 0" ,"VH_scale < 0","VH_scale = 0" ))
```


